\begin{table*}[!htb]
\centering
\small\caption{Shape Additional Effects}
\begin{GenesysTable}{l X}
Cost                                & Effect\\
\difficulty                         & \textbf{Entangle:} All creatures in the affected area are Immobilized.\\
\difficulty                         & \textbf{Range:} Increases the range of the spell by one range band.\\
\difficulty                         & \textbf{Radius:} The size of the area increases by one range band. This may be added again to further increase the size.\\
\difficulty                         & \textbf{Precision:} The character may select one creature within the area to remain unaffected. You may spend one \advantage to select an additional creature.\\
\difficulty\difficulty              & \textbf{Burn:}  All creatures in the area suffer \nameref{iqty:burn} damage equal to the character's ranks in the Knowledge(Nature) skill.\\
\difficulty\difficulty              & \textbf{Rejuvinate:} Rejuvinates the life energies of a patch of land, allowing plants to come back and grow.\\
\difficulty\difficulty\difficulty   & \textbf{Quick Sand:} All characters in the area are Paralysed and immune to all damage. The area is impassable terrain. This cannot be combined with Precision.\\
\difficulty\difficulty\difficulty   & \textbf{Rejuvinate, Large:} Rejuvinates the life energies of a large area of land, allowing plants to come back and grow.\\
\end{GenesysTable}
\label{table:magic_shape}
\end{table*}

\subsubsection{Shape}
\textbf{Skill:} Primal\\
\textbf{Concentration:} Yes\\
\textbf{Basic Difficulty:} \textbf{Average:} (\difficulty\difficulty)\\
Shape spells change the area around them. A druid compels the plants to grow into
aggressive, grasping vines to entangle anything that moves. A wizard creates a
sheets of slippery, flammable grease in the path of her gith persuers.
Pooling their power together, a group of cultists call forth a swirling storm of
spirits that rip at the armor of the adventuring party that seeks to stop them.\\

Shaping magic is how spellcasters exert their will over an entire battlefield.
Though it does little against a single adversary compared to other magic, shapping
magic can effect a wide area for an extended period, completely changing the course
of an encounter. Shaping magic generally does no damage - instead, it restricts
movement. In its most basic form, it turns an area into difficult terrain. As a
rule, shaping magic does not exclude the caster or their allies. All characters
within the affected area suffer its effects unless the caster increases the
difficulty. The caster selects a point within medium range, and everything within
short range of that point is affected.\\

At higher levels a shape spell may immobilize creatures, create an area of total
silence, or simply freeze everything inside a huge block of salt.\\
Before making an Shape check, choose any number of additional
effects from ~\tref{table:magic_shape}.
