\subsection{Adventuring Gear}
\begin{table*}[!htb]
\begin{GenesysTable}{Adventuring Gear}{adventuring-gear}{ =X +l +l +l}
Name                                & Encum & Price & Rarity \\
\nameref{advitm:backpack}           & 0     & 50cp  & 2      \\
Bedroll                             & 1     & 1cp   & 1      \\
Bottle, glass                       & 0     & 10cp  & 1      \\
\nameref{advitm:caltrops}           & 1     & 5cp   & 3      \\
Candle                              & 0     & 10bit & 0      \\
Canvas (m\textsuperscript{2})       & 1     & 1cp   & 1      \\
Chain (3m)                          & 1     & 500cp & 8      \\
Chalk, 1 piece                      & 0     & 5bit  & 1      \\
\nameref{advitm:crowbar}            & 1     & 2cp   & 8      \\
Firewood (per day)                  & 1     & 2cp   & 2      \\
Flask (empty)                       & 0     & 1cp   & 1      \\
\nameref{advitm:grapplinghook}      & 1     & 5cp   & 2      \\
Hammer                              & 0     & 3cp   & 0      \\
Hourglass                           & 0     & 125cp & 4      \\
\nameref{advitm:ink}                & 0     & 100cp & 6      \\
Inkpen                              & 0     & 10cp  & 6      \\
Jug, clay                           & 1     & 1cp   & 0      \\
Ladder, 3m                          & 3     & 1cp   & 1      \\
\nameref{advitm:lamp_common}        & 1     & 1cp   & 1      \\
\nameref{advitm:lantern_bullseye}   & 1     & 65cp  & 3      \\
\nameref{advitm:lantern_hooded}     & 1     & 30cp  & 2      \\
\nameref{advitm:lock}               & 0     & 750cp & 8      \\
\nameref{advitm:manacles}           & 1     & 300cp & 8      \\
Mirror                              & 0     & 50cp  & 3      \\
Mug/Tankard, clay                   & 0     & 1cp   & 0      \\
Musical Instruments, Common         & 1-5   & 50-100cp   & 0 \\
Musical Instruments, High Quality   & 1-5   & 500-1500cp & 0 \\
Musical Instruments, Legendary      & 1-5   & 5000+cp    & 0 \\
\nameref{advitm:oil}                & 1     & 1cp   & 1      \\
Parchment (sheet)                   & 0     & 4cp   & 3      \\
Pick, miner's                       & 2     & 15cp  & 1      \\
Pitcher, clay                       & 1     & 1cp   & 0      \\
Pouch, belt (empty)                 & 0     & 5cp   & 0      \\
\nameref{advitm:poisoner_ring}      & 0     & (R) 500cp  & 7 \\
\nameref{advitm:ram}                & 4     & 10cp  & 6      \\
\nameref{advitm:ration}             & 2     & 20cp  & 1      \\
\nameref{advitm:riding-tack-small}  & 2     & 75cp & 4      \\
\nameref{advitm:riding-tack-medium} & 3     & 100cp & 6      \\
\nameref{advitm:riding-tack-large}  & 5     & 200cp & 7      \\
\nameref{advitm:rope_hemp}          & 1     & 5cp   & 1      \\
\nameref{advitm:rope_silk}          & 1     & 50cp  & 3      \\
\nameref{advitm:saddlebags-small}   & -     & 25cp  & 4      \\
\nameref{advitm:saddlebags-medium}  & -     & 50cp  & 4      \\
\nameref{advitm:saddlebags-large}   & -     & 100cp & 4      \\
Sealing wax                         & 0     & 5cp   & 0      \\
Sewing needle                       & 0     & 3cp   & 1      \\
\nameref{advitm:shovel}             & 1     & 10cp  & 0      \\
Signal whistle                      & 0     & 4cp   & 1      \\
Sledge Hammer                       & 2     & 5cp   & 4      \\
Soap (per 500g.)                    & 0     & 3cp   & 1      \\
Tent, 2ps                           & 2     & 50cp  & 2      \\
Tent, 6ps                           & 4     & 100cp & 2      \\
\nameref{advitm:torch}              & 1     & 1cp   & 0      \\
\nameref{advitm:vial}               & 0     & 5cp   & 0      \\
Whetstone                           & 0     & 1cp   & 1      \\
\end{GenesysTable}
\end{table*}
\begin{multicols}{2}

\paragraph{Backpack} \label{advitm:backpack}
As the name indicates, this is used to carry things around
on one's back - effectively increasing one's encumbrance
threshold.

Backpacks increase the characters encumbrance by 4.

\paragraph{Caltrops} \label{advitm:caltrops}
A caltrop is a four-pronged metal spike crafted so that
one prong faces up no matter how the caltrop comes to
rest. You scatter caltrops on the ground in the hope that
your enemies step on them or are at least forced to slow
down to avoid them. One 1kg bag of caltrops
covers an area 0.5m\textsuperscript{2}.\\
Each time a creature moves into an area covered by
caltrops (or spends a round fighting while standing in
such an area), it runs the risk of stepping on one. Make
an attack roll for the caltrops with no ranks, against the
creature. For this attack defense bonuses do not count. If
the creature is wearing shoes or other footwear, add a
\setback. If the attack succeeds, the creature has stepped on a
caltrop. The target suffers 1 Wound, and the creature
applies the \textit{Hamstrung Critical (The target loses their
free maneuver until this critical is healed)}. This
Daunting (\difficulty\difficulty\difficulty\difficulty)
Brawn check upgrade the
movement penalty lasts for 24 hours, until the critical is
successfully treated, or until it receives at least 1 point
of magical healing.\\
Caltrops may not work against unusual opponents.

\paragraph{Chain} \label{advitm:chain}
A chain. Made from metal, they are rare items, often used to
restrict the movement of arena beasts.
It can be burst with a Formidable
(\difficulty\difficulty\difficulty\difficulty\difficulty)
Brawn check.

\paragraph{Crowbar} \label{advitm:crowbar}
A bar-like object, often made from Mekillot bone, used to
force things open.\\
A crowbar grants a \boost on Athletics checks made to force
open a door or chest. If used in combat, treat a crowbar
as a small improvised weapon.

\paragraph{Grappling Hook} \label{advitm:grapplinghook}
Throwing a grappling hook requires a
Ranged or Coordination check. The difficulty is based on
the range, Medium range being its maximum range.

\paragraph{Ink, 28gr} \label{advitm:ink}
Ink in colors other than black costs twice as much.

\paragraph{Jug, Clay} \label{advitm:jug}
This basic jug is fitted with a stopper and holds 4 liters of liquid.

\paragraph{Lamp, Common} \label{advitm:lamp_common}
A lamp illuminates a Short Range area. A lamp burns
for 6 hours on one pint of oil. You can carry a lamp in
one hand.

\paragraph{Lantern, Bullseye} \label{advitm:lantern_bullseye}
A bullseye lantern provides light up to medium range in
cone. A lantern burns for 6 hours on one pint of oil. You
can carry a lantern in one hand.

\paragraph{Lantern, Hooded} \label{advitm:lantern_hooded}
A hooded lantern illuminates a short range area. A
lantern burns for 6 hours on one pint of oil. You can
carry a lantern in one hand.
This lantern is encased in a more protective cover.
Add a s to any check to put out this light by means of
water or wind.

\paragraph{Lock} \label{advitm:lock}
Daunting (\difficulty\difficulty\difficulty\difficulty) Skulduggery check

\paragraph{Manacles} \label{advitm:manacles}
Restraints made from metal, these things are used only for
the most dangerous of enemies or by the most rich slave- or
bounty-hunters.\\
Manacles can bind a Medium creature. To slip free, a
creature must roll a Formitable (\difficulty\difficulty\difficulty\difficulty)
Coordination Check.  Breaking the manacles requires a
Daunting (\difficulty\difficulty\difficulty\difficulty) Brawn check.
Most manacles have locks; add the cost of the lock
to the cost of the manacles.
For the same cost, you can buy manacles for a Small
creature. For a Large creature, manacles cost 10 times
the indicated amount, and for a Huge creature, 100
times the indicated amount. Gargantuan, Colossal, Tiny,
Diminutive, and Fine creatures can be held only by
specially made manacles, which cost at least 100 times
the indicated amount.
The checks to escape all get setbacks.

\paragraph{Oil, 1 pint flask} \label{advitm:oil}
A pint of oil burns for 6 hours in a lantern or lamp.
You can also use a flask of oil as a splash weapon.
With the proper skill you can use oil as an attack
Roll an Average (\difficulty\difficulty) Alchemy check,
with a base damage of 3 and a burn 1 quality. You
can pour a pint of oil on the ground to cover an
area 0.5m\textsuperscript{2}, provided that the surface is
smooth. If lit,the oil burns for 2 rounds and deals
the base damage of the weapon to each creature in
the area.

\paragraph{Poisoner's Ring} \label{advitm:poisoner_ring}
There are many solutions for those wanting to carry poisons
into restricted areas, and keeping it in a hidden
compartment of jewelry is relatively commonplace.

Holds a single dose of any toxin or drug.

May make an opposed skulduggery check against vigilance
of onlookers to deposit the poison into a meal or drink.

\paragraph{Ram, Portable} \label{advitm:ram}
This iron-shod wooden beam gives you an \boost on
Brawn checks made to break open a door and
allows a second person to help give you \boost\boost
instead of one.

\paragraph{Ration} \label{advitm:ration}
Rations are packages containing everything a person needs
to eat and drink to survive in an wilderness settings.
This includes food and water.

Any day an adventurer in a wilderness setting wishes
to recover either strain or wounds, they need to consume
1 ration.

See \chapterref{rules:survival}.

\paragraph{Riding Tack, Small} \label{advitm:riding-tack-small}
\paragraph{Riding Tack, Medium} \label{advitm:riding-tack-medium}
\paragraph{Riding Tack, Large} \label{advitm:riding-tack-large}
This is simply a saddle, built to be placed on the back
of a beast for ease of riding.
Allows riding of the beast without suffering the bareback penalty.

Medium Riding Tacks are standard while Small ones can be fitted to an Erdlu and Large ones an Inix of Mekillot.

\paragraph{Rope, Hemp (20m)} \label{advitm:rope_hemp}
This rope can be burst with a Hard (\difficulty\difficulty\difficulty)
Brawn check.

\paragraph{Rope, Silk (20m)} \label{advitm:rope_silk}
This rope can be burst with a Hard (\difficulty\difficulty\difficulty\setback)
Brawn check.

\paragraph{Saddlebags, Small} \label{advitm:saddlebags-small}
\paragraph{Saddlebags, Medium} \label{advitm:saddlebags-medium}
\paragraph{Saddlebags, Large} \label{advitm:saddlebags-large}
This simple set of bags are designed to be fitted to the back of a beast.
Can only be worn by riding animals. Increase encumbrance threshold by 4.

Medium saddlebags are standard while Small ones can be fitted to an Erdlu and Large ones an Inix of Mekillot.

\paragraph{Shovel or spade} \label{advitm:shovel}
A simpel shovel with an wooden or bone head. Used to dig
holes in the ground, commonly about 6ft in depth.

It can also be used as a weapon with the following profile;
\begin{table}[H]
\begin{GenesysTable}{Shovel in Melee}{shovel-in-melee}{ =X +l +l +l +l}
Skill 	& Dam 	& Crit 	& Range 	& Special \\
Melee 	& +2 	& 4 	& Engaged   & N/A     \\
\end{GenesysTable}
\end{table}

\paragraph{Torch} \label{advitm:torch}
A torch burns for 1 hour, shedding lighting on
everything within Short Range.
If a torch is used in combat, treat it as a small
improvised weapon with a \iqtyref{burn} 1 quality.

\paragraph{Vial} \label{advitm:vial}
A vial is made out of glass and holds 1 ounce of liquid.

\end{multicols}
\hrulefill

\subsection{Alchemical Items}

\begin{multicols}{2}
\begin{table}[H]
\begin{GenesysTable}{Alchemical Items}{alchemical-items}{ =X +l +l +l}
Name                               & Encum & Price & Rarity \\
\nameref{alcitm:acid}              & 0     & 50    & 2      \\
\nameref{alcitm:alchemistsfire}    & 0     & 100   & 2      \\
\nameref{alcitm:amanita-powder}    & 0     & 500   & 7      \\
\nameref{alcitm:antitoxin}         & 0     & 250   & 3      \\
\nameref{alcitm:healingpoultrice}  & 0     & 10    & 2      \\
\nameref{alcitm:painkilling-spice} & 0     & 80    & 1      \\
\nameref{alcitm:smokestick}        & 0     & 100   & 2      \\
\nameref{alcitm:tanglefootbag}     & 1     & 250   & 3      \\
\nameref{alcitm:thunderstone}      & 0     & 150   & 3      \\
\nameref{alcitm:tindertwig}        & 0     & 5     & 0      \\
\end{GenesysTable}
\end{table}

\paragraph{Acid} \label{alcitm:acid}
You can throw a flask of acid as a weapon with an
Ranged light or Alchemy combat check with a base
damage of 6 acid damage, with a range of short, and
\iqtyref{blast} 3, \iqtyref{sunder}.
It can also be used to damage a lock beyond repair.

\paragraph{Alchemist's Fire} \label{alcitm:alchemistsfire}
You can throw a flask of alchemist’s fire as a weapon
with an Ranged light or Alchemy combat check with
a base damage of 6 fire damage, with a range of short,
and \iqtyref{blast} 3, \iqtyref{burn} 2.

\paragraph{Amanita Powder} \label{alcitm:amanita-powder}
Ground to dust from certain mushrooms grown in caves, this
powder can make one resistant to being tired. However, it
is extremely addictive and builds dependence immediately.

Taken once every 24 hours allows one to not suffer the
penalties from lacking sleep. May remove strain as if
having slept, every 8 hours spent outside an engagement
(combat, intense study or argument). Going without a
dose for longer than 24 hours makes the user extremely
sleepy.

Purple stains appear on the site of application.

\paragraph{Antitoxin} \label{alcitm:antitoxin}
If you drink a vial of antitoxin, you get an upgrade on
your Resilience check against poison for 1 hour.

\paragraph{Healing Poultrice} \label{alcitm:healingpoultrice}
A healing poultrice is a soft moist mass, often heated and
medicated, that is spread on cloth over the skin to treat an
aching, inflamed or painful part of the body. It can be used
on wounds such as cuts. It is a one-use item and provide a \boost
to medicine checks to treat cuts, bruises and minor ailments.

\paragraph{Painkilling Spice} \label{alcitm:painkilling-spice}
This is a powerful substitute for medical painkillers,
however, is toxic enough that the buildup may slow down
the individual's reflexes. It also especially affects those
with psionic abilities, suppressing their abilities.

When consumed, it allows non-psionics to remove 3 setback
dice imposed by pain or illness for 12 hours. It adds a
\threat result on all checks for 24 hours. Psionics
suffer the effects for twice as long and count their Psionics
rating as 1 lower.

\paragraph{Smokestick} \label{alcitm:smokestick}
This alchemically treated wooden stick instantly creates
thick, opaque smoke when burned. The smoke fills a
short range radius, The stick is consumed after 1 round,
and the smoke dissipates naturally after 1 minute.\\
A creature that is engaged range with the fog adds
\setback on Perception, Vigilance, and all combat skill
checks. Creatures farther away looking or targetting into
the mist add \setback\setback to their Perception, Vigilance,
and all combat skill checks.

\paragraph{Tanglefoot Bag} \label{alcitm:tanglefootbag}
tanglefoot bag is a small sack filled with tar, resin
and other sticky substances. When you throw a
tanglefoot bag at a creature roll a Ranged Light or
Alchmey combat check. This attack has a range of
short, does no damage. If successful the attack is treated
as if the wielder activated an \iqtyref{ensnare} 5 quality. The
bag comes apart and goo bursts out, entangling the
target and then becoming tough and resilient upon
exposure to air.

\paragraph{Thunderstone} \label{alcitm:thunderstone}
You can throw this stone as a weapon with an Ranged or
Alchemy combat check with a range of short and deals no damage.
When it strikes a hard surface (or is struck hard), it creates
a deafening bang that is treated as a sonic attack. Each creature
within short range of where it went off must make an Average
(\difficulty\difficulty) Resilence check or be deafened for 1
hour. A deafened creature, in addition to the obvious effects,
takes \setback\setback on initiative rolls and has a \setback
when casting a spell.

\paragraph{Tindertwig} \label{alcitm:tindertwig}
The alchemical substance on the end of this small,
wooden stick ignites when struck against a rough
surface. Creating a flame with a tindertwig is much
faster than creating a flame with flint and steel (or a
magnifying glass) and tinder. Lighting a torch with a
tindertwig is a maneuver (rather than an action), and
lighting any other fire with one is a maneuver.

\end{multicols}
\hrulefill

\subsection{Poisons}\label{chap:poisons}

\begin{multicols}{2}

\begin{table}[H]
\begin{GenesysTable}{Poisons}{poisons}{ =X +l +l}
Name                                & Price & Rarity \\
\nameref{poison:anesthetic}         & (R)  375  & 5      \\
\nameref{poison:befuddle}           & (R)  230  & 6      \\
\nameref{poison:blinding}           & (R)  400  & 8      \\
\nameref{poison:blossomkiller}      & (R)   75  & 6      \\
\nameref{poison:weakness}           & (R)  450  & 8      \\
\nameref{poison:suggestion}         & (R) 1000  & 9      \\
\nameref{poison:paralysis}          & (R)  260  & 6      \\
\nameref{poison:dendriton}          & (R)  150  & 4      \\
\nameref{poison:raquor}             & (R)  150  & 4      \\
\end{GenesysTable}
\end{table}

\paragraph{Anesthetic} \label{poison:anesthetic}
A single dose has an \textbf{Average} (\difficulty\difficulty) difficulty,
while two or more doses combined into a single application have
a \textbf{Hard} (\difficulty\difficulty\difficulty) difficulty The poison
inflicts 5 strain if the target fails the check. If the check
generates one to two \threat, the target must also give up his
free maneuver during his next turn (he may still take two maneuvers,
however); if it generates \threat\threat\threat or more, he's
staggered during his next turn. Finally, the CM can spend \despair
to make the target test against the poison again during the next
round, as the poison remains in his system.

\paragraph{Befuddle Poison} \label{poison:befuddle}
A single dose has an \textbf{Average} (\difficulty\difficulty) difficulty,
while two or more doses combined into a single application have
a \textbf{Hard} (\difficulty\difficulty\difficulty). If the check is
failed the target adds \setback\setback to any \textbf{Intelligence} based
skill check for the next 3 rounds, if the roll results in 1-2
\threat the character also gains \setback on \textbf{Willpower}
checks. If three or more \threat are rolled they upgrade the
difficulty of the next \textbf{Intelligence} check they make by 1. If
\despair is rolled the end check must be made again on the next turn.

\paragraph{Blinding Poison} \label{poison:blinding}
This poison can be ingested, or entered into the bloodstream.
one dose requires an \textbf{Average} (\difficulty\difficulty\difficulty)
resilience check, while 2 doses requires a \textbf{Hard} check. If the target
fails they find it hard to see for 3 turns progressively getting worse,
each round the poison is active they add \setback die to any check
that requires vision.(1 die first turn, 2 second, etc.) if \threat\threat\threat
are rolled, the target also upgrades the difficulty of the same tests
by 1. \despair forces the target to make the check again on their next turn.

\paragraph{Blossomkiller Venom} \label{poison:blossomkiller}
This venom is extracted from the blossomkiller plant. The plant uses
it to paralyse it's victims, after which it can smother it to death
with it's vines.

The venom may only be administered through injection.

To resist the effects, the target must roll a \textbf{Hard} (\difficulty\difficulty\difficulty)
Resilience check. If failed, the target is immobilized for 3
rounds. Every disadvantage from the roll deals 1 strain on the
target, and a critical fail means the poison remains in their
system.

%The venom may only be administered through injection.
%
%The target must succeed an \textbf{Average} (\difficulty\difficulty) Resilience check
%for a single dose, and a \textbf{Hard} (\difficulty\difficulty\difficulty) check for
%anything more than 2 doses.
%
%It deals 5 strain on a failed check. If the check generates 1-2
%\threat, the target cannot make a free maneuver. \threat\threat\threat
%may result in the target being staggered for one turn. A critical failure
%the poison remains in their system.


\paragraph{Poison of Weakness} \label{poison:weakness}
A single dose has an \textbf{Average} (\difficulty\difficulty), while two or more
doses combined into a single application have a
\textbf{Hard} (\difficulty\difficulty\difficulty). On a failed check the
target lowers their brawn trait by 1 for 2 rounds, and suffer 1 strain
for each \threat rolled. A \despair can be spent to make them check for
the poison again in the next round.

\paragraph{Poison of Suggestion} \label{poison:suggestion}
This poison must be ingested to take effect. the victim must make an
\textbf{Average} (\difficulty\difficulty) Resilience check or for the next hour
the target will be extremely susceptible to suggestions made to them.
They will lower the difficulty of all social checks made to convince
them to easy. The gm has discretion to keep the target from harming
themselves or others at a suggestion. If the target rolls \threat\threat\threat
while resisting, they will have a hard time remembering exactly what
happened during the hour they were under the poisons effects, if they
roll \despair they will believe that all suggestions they followed
were their idea. otherwise, once the hour is up they will realize
they have been drugged and act accordingly.

\paragraph{Paralysis Poison} \label{poison:paralysis}
When applied to a weapon (as a maneuver), causes anyone
struck by the poison to make a \textbf{Hard} (\difficulty\difficulty\difficulty)
resilience check on their turn or become immobilized for
the next 3 turns, they also suffer 1 strain per \threat
rolled, and if they roll a \despair they have to make the
check again next round.

\paragraph{Dendriton Poison} \label{poison:dendriton}
\fxnote{Rename to something Athasian}
Dendriton Poison is an exceedingly lethal toxin favoured by assassins who
prefer their victims to suffer. Once exposed to the poison, the victom begins
to suffer fatique and dull pain, which gradually increases until he is
paralyzed and in agony.\\
\\
Any size dose has a \textbf{Daunting} (\difficulty\difficulty\difficulty\difficulty).
If the target fails the check, the poison inflicts 1 strain at the end of his
next turn, 3 strain at the end of his subsquent turn, and 5 strain at the end
of the turn after that one (this ignores soak). In addition, the target sufferts
\setback to any check he attempts while under the effects of the poison, and
each \threat he generates on those checks inflicts 1 dditional strain (ignoring
soak) as the target is wracked with pain and violent muscle spasm. The GM may
spend \despair on the initial Resilience check to make the target make another
check against the poison at the end of his third turn or suffer an additional
5 strain (ignoring soak) as the poison torments him.

\paragraph{Raquor Venom} \label{poison:raquor}
\fxnote{Rename to something Athasian}
Extracted from the glandular toxin sacs of <animal>. Raquor venom is a powerful
paralytic enzyme inhibitor. The Venom has a \textbf{Daunting} (\difficulty\difficulty\difficulty\difficulty).
The poison Staggers the target for 2 rounds if the target fails the check. in
addition, each \threat generated inflicts 2 strain on the target (ignoring soak),
and the GM may spend \despair to Immobilize the target for 2 rounds.

%\paragraph{Bearsloth Venom} \label{poison:bearsloth}
%Extracted from the fearsome Bearsloths of Arbooine, this venom
%is known for its lingering properties in the system of the afflicted.
%
%It is bought in single doses;
%Price 	Encum 	Rarity
%150 	0 	3 (Arbooine Only)
%
%The poison may be administered by injection (bite or scratches too).
%
%The target must make a daunting (\difficulty\difficulty\difficulty\difficulty) resilience
%check. If failed, they receive the "Wracking Venom"
%critical injury (hard [\difficulty\difficulty\difficulty] to heal). Whenever
%the individual would suffer 1 or more wounds or strain; suffer +2.

\end{multicols}
\hrulefill

\subsection{Tools and Kits}

\begin{multicols}{2}

\begin{table}[H]
\begin{GenesysTable}{Tools and Kits}{tools-and-kits}{ =X +l +l +l}
Name                             & Encum & Price & Rarity \\
\nameref{kititm:alchemistslab}   & 5     & 50    & 6      \\
\nameref{kititm:artisanstools}   & 4     & 150   & 0      \\
\nameref{kititm:climberskit}     & 1     & 50    & 2      \\
\nameref{kititm:disguisekit}     & 2     & (R) 100   & 4      \\
\nameref{kititm:healerskit}      & 1     & 100   & 2      \\
\nameref{kititm:thievestools}    & 0     & (R) 100   & 7      \\
\end{GenesysTable}
\end{table}

\paragraph{Alchemist's Lab} \label{kititm:alchemistslab}
This lab is used for making alchemical items, and
provides a \boost on Alchemy checks pertaining to crafting.

\paragraph{Artisan's Tools} \label{kititm:artisanstools}
These special tools include the items needed to pursue
any craft. Without them, you have to use improvised
tools and take a \setback on Crafting checks), if you
can do the job at all.

\paragraph{Climber's Kit} \label{kititm:climberskit}
These crampons, pitons, ropes, and tools give you a \boost check.
on Athletics checks when Climbing.

\paragraph{Disguise Kit} \label{kititm:disguisekit}
The kit is the perfect tool for disguise and provides a \boost
on Deception checks. A disguise kit is exhausted after
10 uses.

\paragraph{Healer's Kit} \label{kititm:healerskit}
This collection of bandages and herbs provides a \boost on
Medicine checks. A healer's kit is exhausted with
\threat\threat\threat or \despair.

\paragraph{Thieves's Tools} \label{kititm:thievestools}
This kit contains lockpicks and other tools you need to
use the Skulduggery skill. Without these tools, you must
use improvised tools, and you take a \setback on Skulduggery
checks, with these tools you get a \boost to a lock or a latch.

\end{multicols}
