\subsection{Armour}

\begin{table*}[!htb]
\centering
\small\caption{Armour}
\begin{GenesysTable}{l l l l l l X}
Name                              & Defense & Soak & Encum & Price  & Rarity & Special  \\
\nameref{itmamr:heavyrobes}       & 1       & +0   & 1     & 5cp    & 1      & \\
\nameref{itmamr:hardenedleather}  & 0       & +1   & 2     & 10cp   & 1      & \iqtyref{flimsy} \\
\nameref{itmamr:scalemail}        & 1       & +1   & 2     & 25cp   & 3      & \iqtyref{fragile} \\
\nameref{itmamr:chitinarmor}      & 0       & +2   & 3     & 50cp   & 4      & \iqtyref{fragile}, \iqtyref{solid} 1 \\
\nameref{itmamr:shellarmor}       & 1       & +2   & 3     & 100cp  & 5      & \iqtyref{fragile}, \iqtyref{noisy}, \iqtyref{solid} 2 \\
\nameref{itmamr:breastplate}      & 1       & +2   & 3     & 200    & 6      & \iqtyref{fragile}, \iqtyref{noisy} \\
\nameref{itmamr:halfplate}        & 1       & +3   & 4     & 600    & 7      & \iqtyref{fragile}, \iqtyref{noisy}, \iqtyref{restrictive}, \iqtyref{solid} 2 \\
\nameref{itmamr:fullplate}        & 2       & +3   & 5     & 1250cp & 8      & \iqtyref{fragile}, \iqtyref{noisy}, \iqtyref{restrictive}, \iqtyref{solid} 3 \\
\end{GenesysTable}
\end{table*}
\begin{multicols}{2}

\subsubsection{Heavy Robes}
\label{itmamr:heavyrobes}
These are robes made of multiple layers of thick robe.

\subsubsection{Hardened Leather}
\label{itmamr:hardenedleather}
This armor is crafted using close-set rivets made of bone, hardwood, stone, or talons.

\subsubsection{Scale mail}
\label{itmamr:scalemail}
Scale mail is usually made from the scales of an erdlu, inix or other naturally scaled creatures.

\subsubsection{Chitin Armor}
\label{itmamr:chitinarmor}
This armor is skillfully made by interlocking hexagonal bits of chitin (usually carved from a kank’s carapace).

\subsubsection{Shell Armor}
\label{itmamr:shellarmor}
Shell armor is made by weaving giant's hair around the shells of various small creatures such as an aprig.

\subsubsection{Padded Armor}
\label{itmamr:paddedarmor}
Padded armor is made of heavy cloth and batting. Many Athasian warriors prefer padded armor woven from giant hair.

\subsubsection{Breastplate}
\label{itmamr:breastplate}
These armors are constructed using choice plates taken from shelled animals, such as mekillots or braxat.

\subsubsection{Half Plate}
\label{itmamr:halfplate}
These armors are constructed using choice plates taken from shelled animals, such as mekillots or braxat.

\subsubsection{Full Plate}
\label{itmamr:fullplate}
These armors are constructed using choice plates taken from shelled animals, such as mekillots or braxat.

\end{multicols}
