\subsubsection{Mounts}
\begin{multicols}{2}

Athasians have domesticated a variety of mounts. The
most common are presented below. More unusual
steeds, such as giant ants, spiders, drakes, and
wyverns can be found, but not easily or cheaply.

\begin{table}[H]
\begin{GenesysTable}{Mounts}{mounts}{ =X +l +l +l +l}
Name                       & Speed & Encumbrance & Price    & Rarity \\
\nameref{itmmnt:crodlu}    & 7     & 10          & 2250cp   & 3      \\
\nameref{itmmnt:warcrodlu} & 7     & 10          & 9500cp   & 6      \\
\nameref{itmmnt:erdlu}     & 7     & 10          & 750cp    & 2      \\
\nameref{itmmnt:kank}      & 7     & 10          & 8400cp   & 7      \\
\nameref{itmmnt:inix}      & 5     & 10          & 11000cp  & 5      \\
\nameref{itmmnt:mekillot}  & 6     & 10          & 40000cp  & 8      \\
\end{GenesysTable}
\end{table}

\paragraph{Crodlu}
\label{itmmnt:crodlu}
A crodlu is a large, flightless drake with a beak and
weak, clawed forelimbs that can be used to manipulate
small objects. It is a tough and aggressive hunter
in the wild. See \nameref{creature:Crodlu} for more
information.

\paragraph{War Crodlu}
\label{itmmnt:warcrodlu}
A crodlu is a large, flightless drake with a beak and
weak, clawed forelimbs that can be used to manipu-
late small objects. It is a tough and aggressive hunter
in the wild. When trained, it makes an excellent war
mount. See \nameref{creature:War Crodlu} for more information.

\paragraph{Erdlu}
\label{itmmnt:erdlu}
The erdlu is a smaller version of the crodlu. Its body
is covered in tough scales, and its folded forelimbs
sprout useless wings. Hardy and fast, this drakelike
creature is a fine riding beast for a Silhoutte 0 rider.
It is too skittish to be trained for war, however. See
\nameref{creature:Erdlu} for more information.

\paragraph{Kank}
\label{itmmnt:kank}
Kanks are docile insects that form hives. Each member
of the group has a role: food producer, soldier, or
the brood queen. The kank soldier can be trained for
riding and battle. See \nameref{creature:Kank Mount} for
more information.

\paragraph{Inix}
\label{itmmnt:inix}
An inix, also called a dune behemoth, is a long, low-
slung reptile with bony plates on its back. It is strong
and spirited. An inix rarely eats anything as large as
a humanoid, but it does not shy away from a fight. See
\nameref{creature:Inix} for more information.

\paragraph{Mekillot}
\label{itmmnt:mekillot}
These massive creatures serve as draft animals
given their tremendous pulling strength. They are
aggressive, however, and have been known to turn
on handlers. See \nameref{creature:Mekillot} for
more information.

\end{multicols}
