\subsection{Ranged Weapons}

\begin{table*}[!htb]
\centering
\small\caption{Ranged Weapons}
\begin{GenesysTable}{l l l l l l l X}
Name                      & Dam & Crit & Range  & Encum & Price    & Rarity & Special \\
\nameref{itmrng:blowgun}  & 6   & 3    & Short  & 2     & 275 cp   & 3      & \iqtyref{limitedammo} 1\\
\nameref{itmrng:bolas}    & +0  & -    & Short  & 1/3   & 20 cp    & 2      & \iqtyref{ensnare} 3, \iqtyref{knockdown}, \iqtyref{limitedammo} 1 \\
\nameref{itmrng:catkcha}  & +2  & 4    & Short  & 1     & 275 cp   & 4      & \iqtyref{fragile}, \iqtyref{unwieldy} 3, \iqtyref{returning}, \iqtyref{limitedammo} 1 \\
\nameref{itmrng:javelin}  & +2  & 3    & Short  & 1/3   & 40 cp    & 1      & \iqtyref{fragile}, \iqtyref{accurate} 1, \iqtyref{pierce} 1, \iqtyref{limitedammo} 1 \\
\nameref{itmrng:dejada}   & 5   & 3    & Medium & 2     & 275 cp   & 2      & \iqtyref{unwieldy} 2, \iqtyref{concussive} \\
\nameref{itmrng:shortbow} & 7   & 3    & Medium & 2     & 275 cp   & 3      & \iqtyref{unwieldy} 2 \\
\nameref{itmrng:longbow}  & 8   & 3    & Long   & 2     & 275 cp   & 5      & \iqtyref{unwieldy} 3 \\
\end{GenesysTable}
\end{table*}
\begin{multicols}{2}

\subsubsection{Blow Gun}
\label{itmrng:blowgun}
Blowguns are generally used to deliver debilitating (but rarely fatal) poisons from a distance. They are nearly silent when fired.

\subsubsection{Bolas}
\label{itmrng:bolas}
A bola consists of a couple of round stones joined together by a strong string of rope. Skilled throwers can use them to catch or trip prey from a distance.

\subsubsection{Catkcha}
\label{itmrng:catkcha}
This throwing wedge, often shaped from crystal or obsidian, is a thri-kreen invention. It returns to a proficient wielder’s hand after the ranged attack is resolved.

\subsubsection{Dejada}
\label{itmrng:dejada}
A long, scooped basket fitted to a glove-like bracer, the dejada is used to hurl projectiles. Ammunition can be a fist-sized stone, but the weapon is also used to extend the range of alchemical mixtures.

\subsubsection{Javelin}
\label{itmrng:javelin}
A javelin is a thin throwing spear.

\subsubsection{Long Bow}
\label{itmrng:longbow}
At almost 5 feet in height, a longbow is made up of one solid piece of carefully curved wood.

\subsubsection{Short Bow}
\label{itmrng:shortbow}
A shortbow is made up of one piece of wood, about 3 feet in length.

\end{multicols}
