\Creature[name=Kank Worker, type=Minion, intellect=0, presence=1, soak=3, wounds=6, meleedef=0, rangeddef=0, magicdef=0, psionicdef=0]
{
    % description
    \textit{
        This creature is a large insect with a black, chitinous
        exoskeleton and long, waving antennae. Its body is divided into
        a head, thorax and abdomen, and it has a pair of curved
        mandibles with which it produces a curious clicking noise.
    }\\
    \\
    Many kanks roam wild across the Tablelands, as well
    as being herded. These large, docile insects have black
    chitinous exoskeletons, which are divided into three
    sections: head, thorax, and abdomen. They can carry
    objects with their multi–jointed pincers, or use them in
    combat.\\
    \\
    A worker only goes into combat when all the soldiers
    are dead or it is backed up into a corner. Workers strike
    with their pincers when in combat and try to get a hold.
}{
    % skill
    Brawl, Perception
}{
    % talents
}{
    \\ % ability
    \textbf{- Grapple: } A Kank may spend \advantage\advantage after an attack
     and enemies must spend two maneuvers to disengage tfrom your character.\\
}{
    \\ % equipment
    \textbf{- Pincer Strike: } Brawl; Damage: 4; Critical: 5; Range [Engaged], Grapple\\
}

\Creature[name=Kank Soldier, type=Rival, brawn=3, intellect=0, presence=1, soak=4, wounds=13, meleedef=0, rangeddef=0, magicdef=0, psionicdef=0]
{
    % description
    \textit{
        This creature is a large insect with a black, chitinous
        exoskeleton and long, waving antennae. Its body is divided into
        a head, thorax and abdomen, and it has a pair of curved
        mandibles with which it produces a curious clicking noise.
    }\\
    \\
    With powerful mandibles and a poisonous bite,
    soldier kanks are the warriors of their hive. When
    domesticated, soldier kanks are often used as caravan
    mounts, as they can travel for a full day at top speed
    while carrying a tremendous amount of weight for their
    size.\\
    \\
    A soldier is the first line of defense for the hive. A
    soldier strikes with its pincers when in combat and tries to
    get a hold. A soldierʹs bite is poisonous.
}{
    % skill
    Brawl 3, Perception 2
}{
    % talents
}{
    \\ % ability
    \textbf{- Grapple: } A Kank may spend \advantage\advantage after an attack
         and enemies must spend two maneuvers to disengage from a kank.\\
    \textbf{- Poison: } If the attack deals damage, the target must immediately make a
        Hard(\difficulty\difficulty\difficulty) Resilience check or suffer 1 wound per turn.
        The target can me another \textbf{Hard} (\difficulty\difficulty\difficulty) check
        at the end of each round to stop the poison. An \nameref{alcitm:antitoxin} or
        \textbf{Average} (\difficulty\difficulty) medicine check will also stop the poison.\\
}{
    \\ % equipment
    \textbf{- Pincer Strike: } Brawl; Damage: 5; Critical: 5; Range [Engaged], Grapple, Poison\\
}
