\subsection{Belgoi}

\subsubsection{Manual Laborer (+0,+0,+0)}

Manual laborers may be farmers, peasants, or others
with access to pitchforks, shovels, sledgehammers, or
other tools they can use as improvised weapons.
Weapons: Large farming implement (Melee [Heavy];
Damage +3; Critical 5; Range [Engaged]; Cumbersome
3, Inferior).
Equipment: Heavy clothes (+1 soak).

\subsubsection{Citizen (+0,+0,+0)}
In every setting, there are multitudes of average people
simply living out their lives. This equipment package is
for any character who has no reason to have weapons,
armor, or specialized gear.

Weapons: Fists (Brawl; Damage +0; Critical 6; Range
[Engaged]; Disorient 1, Knockdown).
Equipment: Clothing appropriate to the specific era,
average coin purse or wallet.

\subsubsection{Crafter (+0,+0,+1)}
Those who build, repair, work outdoors, and work with
their hands have access to various tools or scrap that
can be used as a weapon in a pinch.

Weapons: Improvised brawling weapon (Brawl; Damage
+1; Critical 5; Range [Engaged]; Disorient 2, Inferior).
Equipment: Heavy clothing (+1 soak), tool belt full of
tools (add to checks this character makes to repair of
fix something), wallet.

\subsubsection{Crimincal (+1,+0,+1)}
Muggers, bandits, and thieves are all possible criminals.
Weapons: Concealable melee weapon (Melee [Light];
Damage +1; Critical 2; Range [Engaged]; Pierce 2).
Equipment: Dark clothing (2 defense, adds \boost to
Stealth checks this character makes), thieves’ tools (add
\advantage to Skulduggery checks this character makes to open
locks), backpack, rope with grappling hook.

