\subsection{Plants}

\Creature[name=Blossomkiller, type=Rival, brawn=3, agility=0, intellect=0, presence=0, soak=1, wounds=10, meleedef=0, rangeddef=0, magicdef=0, psionicdef=0]
{
    The Blossomkiller is a very unique plant found in all the vegetated
    areas of Athas. The plant has many different features, including
    its stalk, roots, tendrils, and flowers.

    A single blossomkiller plant occupies an area with a radius of
    up to 15 meter. The roots and vines of this plant stretch across the
    area, between, in, and around any other nearby plants. The
    stalk of a blossomkiller is the size of a large tree trunk, but as it
    grows it lays flat down on the ground, where it spreads out in all
    directions.

    When a victim steps on any of the plants roots, the flowers shoot a
    spray of quills in all directions, entirely covering the area occupied
    by the plant. The quills carry on them a natural paralysis poison, and
    any creature or being hit by them is affected by \nameref{poison:blossomkiller}.
    Those who succeed take 2 points of Strain, but are otherwise unaffected.
}{
    % skill
    Ranged 4
}{
    % talents
    None
}{
    \\ % ability
    \textbf{- Shoot Quills: } As a reaction on being stepped on, a
        Blossomkiller will shoot quills in all direction. This is
        treated as a ranged attack with \iqtyref{blast} 2, Damage 0,
        Range: Engaged. This attack will do no damage, by anyone
        successfully hit will be affected by \nameref{poison:blossomkiller}.
    \textbf{- Vines: } When a target is paralyzed, the Bloomkiller can,
        as an Action, move to wrangle the target with it's vines. These
        Do Brawn +2 Strain Damage, \iqtyref{pierce} 1, \iqtyref{ensnare}.
}{
}
