\chapter{Magic}\label{chap:magic}

\epigraph{\textit{
    "The Tablelands are a giant wasteland, to the untrained eye barren and devoid of life. When people see plants wither and
    die when someone utters mysterious phrases accompanied by unknown gestures, they assume the worst. They cry wizard
    and the mob instantly gathers to kill him. But if people venture into the wastes and look under the rocks, they will learn
    that Athas is teeming with all sorts of life. And when the vermin swarm forth to envelop them, biting and crawling into
    every orifice, do they see the irony?" } } { The Oracle, Blue Shrine Scrolls }


\begin{table*}[!htb]
\centering
\small\caption{Penalties when casting spells}
\begin{GenesysTable}{X X}
Condition                                                       & Penalty\\
The character does not have a free hand                         & +\setback \\
The character is gagged, silenced or otherwise unable to speak  & +\setback\setback \\
Penalty per 1 encumbrance or armor above 1                      & +\setback \\
The character is in circumstances that interfere
with their ability to concentrate, such as trying
to cast while swimming or hanging from a rope,
being buffeted by a sandstorm, or casting a spell
that doesn't target the person they're fighting in
hand-to-hand combat.                                           & +1 or more \difficulty \\
\end{GenesysTable}
\end{table*}

\begin{table*}[!htb]
\centering
\small\caption{Spending Threat and Despair when casting spells}
\begin{GenesysTable}{l X}
Cost                               &    Result\\
\threat or \despair                &    The magical energies exhaust the player, they suffer 2 strain or 1 wound (GM's choice)\newline
                                        \newline
                                        (When using the Defiling action) Plantlife in the area turns to ash. Using more \threat or \despair upgrades the area, or even includes wildlife.
                                        This is narrative penalty and can include the attention of creatures who are quite unhappy with the state of the new area.
                                        \newline
                                        All arcane and primal casters, including the caster, suffer \setback untill this players next turn \\
\threat\threat or \despair         &    The spell doesn’t take effect until the start of the next round, or after a minute in narrative gameplay.\newline
                                        \newline
                                        Until the end of the encounter, enemy spellcasters add \boost when casting a spell that targets this character.\\
\threat\threat\threat or \despair  &    The spell is slightly more powerful than expected. One character of the GM's choice is targeted or otherwise affected by the spell as well.\newline
                                        \newline
                                        All other spellcasters and creatures attuned to magical energies within a day's travel become aware of the character (and depending on
                                        their disposition, may be very interested in finding them and doing them harm). \\
\despair                           &    The character overexerts themself or loses their magical connection and is unable to cast spells for the rest of the encounter or scene.\newline
                                        \newline
                                        The GM picks the target of the character's spell. If the caster is an NPC, the controlling player picks the target of the spell instead.\\
\despair\despair                   &    The character completely lose control of their magical energies or draws the ire of their deity, suffering one Critical Injury (at the GM's
                                        discretion, this may instead take the form of some of terrible or hilarious misfortune, such as temporarily being turned into a small woodland
                                        creature, being struck by lightning on a clear day, swapping bodies with someone else in the encounter for the remainder of the day, or
                                        summoning an avatar of divine or infernal wrath).\newline
                                        \newline
                                        (When using the Defiling action) A ally of the player gains a number of wounds equal to the number of \threat rolled.
                                        \newline
                                        If the caster is using an component from an component pouch, the pouch is now empty, and as to be refilled.\\
\end{GenesysTable}
\end{table*}

\begin{multicols}{2}
\section{Arcane}
Both Arcane and Primal are skills, and are considered arcane magic. The
difference between the two is spell access.  Characters can only use the
Arcane or Primal skill to cast a spell if they have a talent allowing
such use. Each spell has various options to raise the overal difficulty
of the check, in exchange for various benefits. The overal difficulty of
such a check can never be raised beyond Formidable
(\difficulty\difficulty\difficulty\difficulty), after reductions.

Casting a spell uses the requires using a~\textit{'Cast Spell'}
Action, of which there are 2 variants.

\subsection{Magical Actions}
\subsubsection{Cast Spell (Defiling)} \label{action:defliling}
Magic uses the energy of the environment and when a spell caster is unwilling or
unable to supplement use their own energies, she has to draw all the energies
needed from the environment. This has a devastating effect on the local area.
When Defiling you gain a number of automatic \threat equal to the difficulty of
the spell. \textit{These do not cancel any \advantage rolled by the player nor
are they canceled by any. The player can choose to cancel any number of \threat
with advantages, including zero}. Unlike \textbf{Cast Spell (Preserving)}, there is no strain cost
associated with this action, and any \threat or \despair rolled in the check
or gained by using this action, cannot be used to cause strain or wounds upon the
caster. These \threat and \despair can be used as a narrative element. These can
range from turning local plantlife to ash in a small radius op to draining entire
areas of life. This should be scaled to the number of \threat and \despair rolled
in the check must be used to strengthen the effect.

\subsubsection{Cast Spell (Preserving)} \label{action:preserving}
Preservers try to minimise the damage to animal and plant life and use
only part of the magical energies needed to cast a spell from the environment.
The rest of the magical energies needed are supplemented from their own bodies.
However, when there is an abundant amount of life in the neighberhood it is
easier to avoid permanent damage to the environment and thus it is less taxing
to the preservers' body.  Using this action to cast a spell costs up a number of
strain equal to the final difficulty of the spell Advantages from checks after
this one cannot be used to recover this strain but can be used to recover existing
strain.

\subsection{Magical Manouvers}
To use these manouvers, the character has to have atleast 1 rank in either
the Arcane or the Primal skills and have a talent allowing them to use that
skill to cast spells.

\subsubsection{Counterspell}
Most skilled mages or spellcasters can attempt to counter an opponent’s spells
as they are being cast. If the character performs the counterspell maneuver,
all opponents within medium range upgrade the difficulty of checks to cast
spells once, until the end of the character's next turn.
\subsubsection{Concentrate}
Some magical effects might require concentration to sustain. If a magical action
(or spell) can benefit from concentration, the action description notes this.
Spells that can be sustained through concentration last until the end of the
character's next turn (as noted in their description). However, if the character
performs the concentrate maneuver during that next turn, the spell’s effects last
until the end of the character’s following turn, instead. This can be sustained
indefinitely by performing the concentrate maneuver each turn.

\end{multicols}
\begin{multicols}{2}
\subsection{Arcane Spells}
\input{magic/spells/attack}
\input{magic/spells/barrier}
\input{magic/spells/dispel}
\input{magic/spells/illusion}
\input{magic/spells/utility}
%\input{magic/spells/enchantment}
\end{multicols}
\begin{multicols}{2}

\subsection{Primal Spells}
\input{magic/spells/augment}
\input{magic/spells/conjure}
\input{magic/spells/curse}
\input{magic/spells/shape}

\FloatBarrier

\section{Psionics}
Your rank in the Psionics skill determines your psionics rating.
When using a psionics power, you roll a number of \force die equal to your
psionics rating. You can use \darklight to enhance your psionics power,
using \light is free, however \dark points show that you have a harder time,
if you want to use \dark points, you lose 1 strain for each \dark point you
use.

In contrast to the Arcana and Primal skills, anyone with one or more ranks
in Psionics can buy and use a Psionics Power, as listed below.

\end{multicols}
\newpage
\input{magic/psionics/bind}
\input{magic/psionics/enhance}
\input{magic/psionics/farsight}
%%\input{magic/psionics/imbue}
\input{magic/psionics/influence}
\input{magic/psionics/move}
\input{magic/psionics/sense}
