\chapter{Roleplaying}\label{chap:roleplaying}
"I live in a world of fire and sand. The crimson sun scorches the life from anything that crawls or flies, and storms of sand scour the foliage from the barren ground. This is a land of blood and dust, where tribes of feral elves sweep out of the salt plains to plunder lonely caravans, mysterious singing winds call travelers to slow suffocation in the Sea of Silt, and selfish kings squander their subjects’ lives building gaudy palaces and garish tombs. This bleak wasteland is Athas, and it is my home." — The Wanderer’s Journal

I've compiled a few lists of things that most characters would know to use as a player handout in my games. During character creation, hand out each section that applies to each character (race, social class, city state) as they are chosen, the others that don't get used can be quick reference guides for things like knowledge checks, or info for when players interact with NPCs and are asking questions.

General

    There are no gods
    A full skin or pot of water is worth your life
    You can’t trust an Elf
    Athas is an endless wasteland, spotted by tiny oases, and filled with predators
    The desolate condition of Athas is the result of unchecked magic use
    Arcane spellcasters are mistrusted at best, and reviled more often than not
    The tablelands are dotted with ruins from an ancient past
    Every creature, and even a few plants have some form of latent psionic power
    There are seven city states: Balic, Draj, Gulg, Nibenay, Raam, Tyr, and Urik, each ruled by an oppressive Sorcerer King
    Even more powerful than the Sorcerer Kings is The Dragon, who demands tribute of 1000 slaves from each city state each year

Dwarves

    Nothing comes before family except your Focus
    A Dwarf’s chief love is toil
    If a Dwarf dies with his Focus incomplete, he returns as an undead Banshee to haunt the objective of his Focus
    Dwarves are hairless and consider the very idea of hair repulsive, though carvings at the Dwarven city of Kled show Dwarves sporting hair and beards in the ancient past
    The three primary Dwarven settlements are North and South Ledopolus, and Kled, a Dwarven village near the City State of Tyr
    The Dwarves of North and South Ledopolis are trying to build a bridge to connect the two villages, but the giants living on Ledo Island in the center keep wading out across the Silt Sea to destroy the bridge
    Dwarves shun arcane magic as a rule, and while they will travel with a spellcaster who proves themselves a worthy companion (by actively working towards the Dwarf’s Focus), they rarely ever fully trust a wizard
    Dwarves who study The Way tend to excel in its use, and many Dwarves become Clerics of Earth, while Fire and Water also tend to attract Dwarven devotees.
    Dwarves almost always have a serious, sober demeanor. Only when they’ve completed their Focus do they allow other Dwarves, and their most trusted non-Dwarven friends see their joy and sense of humor (and that lasts only until another Focus is chosen)
    Nothing is impossible in the eyes of a Dwarf. The fastest way to earn the enmity of a Dwarf is to tell him “It can’t be done.”

Elves

    “Death is stillness, so run, you Elves. Dance to the beat of life, for the moment is quick and oh so short. There is nothing as fast nor as proud nor as wonderfully made as an Elf.”
    You can’t trust anyone, especially outside your own tribe (until they’ve passed a series of trust tests)
    Those that fall behind are left behind
    To ride rather than run is to have no honor
    Of all the races, Elves are the most likely practitioners of sorcery, particularly Defiler magic
    Elves do not usually excel in the pursuit of Psionics, because most lack the dedication to continue their studies.
    Elves live for the “now”. They have little care for anything but instant gratification. Looking back the past reminds them of lost opportunities for fleeting happiness, while the future is almost certainly going to be worse than now.
    Elves revere Coraanu Star Racer, the Warrior Thief and mythical “first elf” as a pinnacle of Elvishness to aspire to.
    Elves will often flaunt a stolen item right in front of its former owner. Elven culture dictates the victim should congratulate the Elf on the possession of such an attractive item. Those who do not are considered poor sports.
    Elven chiefs are customarily given a percentage of the gains from any raid. An Elf who holds out on his chief is considered disloyal to his tribe.

Halflings

    Death is preferable to slavery
    Wages are a form of slavery
    Halfling speech is riddled with idioms and cultural references
    Halflings have a very rich and diverse culture
    Halflings are more concerned with how their deeds help improve Halfling culture, rather than amassing great treasures
    Halflings are mainly carnivorous and prefer their meat raw
    Halflings are very concerned with the condition of the environment and will take any measure to keep their jungle from becoming like the rest of the tablelands
    Halflings have little to no concept of conquest and plunder in their culture
    Halflings don’t require as much food or water as the larger races
    Halfling chiefs are much like the Sorcerer Kings of the great city states, but are all Preservers rather than Defilers

Half-Elves

    Half-Elves pride themselves on their self-reliance
    Most Half-Elven children are usually abandoned by their Elven parent
    Half-Elves almost always have human names, most being unable to earn a proper Elven name.
    Half-Elves predominantly live within human society, or out in the wilderness as hermits as they have no separate culture of their own
    Half-Elves readily take to studies and professions that favor solitary independence. Magic, Psionics, and the element of Water all are common pursuits.
    Half-Elves also become Druids quite often due to their natural inclination towards solitude
    Half-Elves often find the Templarate a fitting life.
    Many Half-Elves resent Elves, yet also feel a need to win their approval
    A Half-Elf is just as likely to seek companionship from an animal as they are from another person
    Due to their heightened senses and the fact that they are usually more reliable than Elves, many Half-Elves are hired by merchant caravans as scouts and outriders

Half-Giants

    You have no culture/cultural identity of your own, so you readily adopt the culture and behavior of those you admire
    Despite their size and fearsome reputation, Half-Giants tend to possess an almost child like friendliness and curiosity
    Half-Giants also have a ferocious temper, only a fool would tempt a Half-Giant’s rage
    Half-Giants rarely have the patience or mental facilities for learning magic or psionics, though the occasional clever Half-Giant might dabble with Metacreativity or Psychokinesis and become a truly terrifying psychic warrior
    Half-Giants rarely become leaders, more often than not they follow an admired or charismatic friend into adventure, or whomever they find particularly interesting
    Half-Giants require twice as much food and water as other demihumans
    Your large size sometimes causes you to accidentally break human-sized dwellings and furniture
    Most Half-Giants live their lives as slave soldiers, though the more ambitious and adventurous among them sell their services as highly sought after mercenaries
    If you meet someone interesting enough, you might completely abandon whatever it is you’re doing to follow them
    Legend has it a great Sorcerer King created your race long ago.

Humans

    Humans are ubiquitous in the tablelands of Athas
    Humans are the most adaptable among races and fill stations from the lowliest slaves and hermits to the rulers of the great trading houses and high templars of the Sorcerer Kings themselves.
    Humans take readily to studying The Way, as well as the worship of the elements.
    Most humans distrust and fear arcane magic. Many wizards, both preservers and defilers, have been killed by an angry mob.
    There is nothing human ingenuity cannot accomplish.

Muls

    You were born a slave, and you will likely die a slave
    Most Muls are kept as gladiator slaves, due to their nearly unmatched physical prowess
    The life of a gladiatorial slave can be almost as lavish as that of the nobility, if you continue to perform well
    While many Muls have the opportunity to win their freedom many choose to remain in the arenas
    You are stronger than the other races, what would be considered intolerably painful for others is only a mere distraction for you
    Your stamina is unparallelled. You can quarry rock for a full 12 hours with no rest or walk for days without stopping. As long as you sleep at least 6 hours every few days, you don’t suffer from fatigue.
    Unlike the Dwarves they are descended from, Muls often sport tattoos, from shoulder markings denoting victory in the arenas to full body tattoos.
    Most Mul births result in the death of the mother, especially if the mother is human.
    Muls are born sterile and can have no children.
    Despite their formidable physique Muls don’t always make good soldiers. They’re smart enough to tell when a commander is making a tactical error, and stubborn enough to refuse such orders.

Thri-kreens

    Elves are tasty
    Humanoid customs are strange, and most of the time none of the other races seem to understand Thri-kreen ways.
    Thri-kreen have a pack mentality, and tend to view everything from a predator/prey point of view.
    Many Thri-kreen develop psionic powers beyond a simple wild talent, they make excellent Monks and Psionicists
    Some Thri-kreen are capable of delivering a poisonous bite
    Thri-kreen possess great agility and can leap great distances
    Since you do not sleep, you don’t understand why other races seem to become lazy during certain parts of the day
    You live for the hunt, little else interests you
    Thri-kreen have no disposition towards magic, especially arcane
    There are no known Thri-kreen settlements within the tablelands

Freeman

    Templars can enter your home at will
    While you are not a slave, you must devote most of your time to earning enough money to keep your freedom
    Most freemen are crafters and artisans, others run market stalls or smaller businesses like taverns and brothels in the less savory parts of the city
    Most freemen own at least a small home
    Very occasionally a freeman is successful (or lucky) enough to rise into the ranks of nobility through sheer wealth

Noble

    You have been born into a life of luxury, but also one of political intrigue
    You never set foot outside of the safety of your villa or compound without your guards, palanquin to ride in, or at the very least a good disguise.
    You have slaves to deal with the things lesser people have to do themselves
    Many nobles have personal bards, consorts, and other “toys” to keep them occupied.
    A favorite pastime of the nobility is betting on their favorite gladiator(s)

Slave (Artist)

    You are a slave. You were either born into slavery, could not pay a debt, or were caught committing a crime and were sold into slavery.
    Your owner/master may have taught you how to read and write, but this skill is illegal in all of the city states, and will likely get you killed if anyone finds out
    The best way to stay alive is by creating whatever type of art keeps your master happy
    You live a lavish lifestyle for a slave, rivaled only by gladiatorial champions
    Attempted escape carries a penalty of death

Slave (Farmer)

    You are a slave. You were either born into slavery, could not pay a debt, or were caught committing a crime and were sold into slavery.
    To earn your freedom, you have to work off your debt
    When you aren’t working you are sleeping, you have little time for anything else
    If you move your hand to your mouth without permission while working in the fields, you will lose a hand. If it happens again, you will be beaten to death.
    Attempted escape carries a penalty of death

Slave (Gladiator)

    You are a slave. You were either born into slavery, could not pay a debt, or were caught committing a crime and were sold into slavery.
    Your purpose is to fight for the entertainment of others, sometimes to the death
    The life of a gladiatorial slave can be almost as lavish as that of the nobility, if you continue to perform well
    You can win/buy your freedom if you are good. If you aren’t, you will likely end up pitted against a superior opponent so that your death can entertain the crowds
    Attempted escape carries a penalty of death

Slave (Laborer)

    You are a slave. You were either born into slavery, could not pay a debt, or were caught committing a crime and were sold into slavery.
    To earn your freedom, you have to work off your debt
    When you aren’t working you are sleeping, you have little time for anything else
    All you know of life is either toiling day in and day out in a mine or quarry, or building something for your master
    Attempted escape carries a penalty of death

Slave (Soldier)

    You are a slave. You were either born into slavery, could not pay a debt, or were caught committing a crime and were sold into slavery.
    To earn your freedom, you have to work off your debt by completing your term of deployed service
    Attempted escape carries a penalty of death
    Most of your life is spent in the training yards, preparing for war
    When battle comes, you can be sure to be placed on the front lines where fighting is the fiercest and mortality rates are staggeringly high

Tribal (can be used in place of both social standing, as well as city state)

    City states seem claustrophobic to you, everything is too close, there are too many people, and they stink of shit.
    Whether a tribe of nomadic herdsmen, hunter-gatherers, or raiders, you are often on the move, never staying put for too long.
    You have seen things out in the wastelands of Athas that most people in the cities couldn’t even comprehend.
    Most tribes, regardless of vocation, tend to be comprised of a single race. The exception to this, of course, are the tribes of escaped slaves.
    In most tribes the leader is the strongest individual, and changes in leadership tend to be violent.

Balic (based on ancient Greek and Roman culture)

    Andropinis claims he was elected to the position of lifelong dictator over 700 years ago
    Templars in Balic are elected for 10-year terms. Andropinis usually makes it clear which ones he favors, and on the rare occasion that the “wrong” one wins, they disappear
    Andropinis’ personal army consists of 10,000 mostly human foot soldiers carrying lances, large wooden shields, and bone daggers (hoplites)
    Every citizen of Balic is a member of the militia and spends every 10th month assisting the regular army patrol the fields to reduce crop and stock loss to Giants who regularly raid from across the Silt Sea
    Balic is situated in the Estuary of the Forked Tongue, a very defensible location as far as invasion from the other city-states is concerned, as it is surrounded by parts of the Silt Sea on the North, East, and South sides
    Balic has a strong economic district, which specializes in trade of olive oil, kank nectar, and pottery.
    The Agora, or market square is completely ringed in by the Elven market, making it impossible to do any legitimate business without dealing with the dubious offers of the Elven merchants
    The Silt Sea contains numerous islands inhabited by giants, and dotted with crumbling ruins.
    Shipfloaters are psionicists who telepathically levitate ships to traverse the Sea of Silt.
    Rumor: The Dwarves of North and South Ledopolis are trying to build a bridge to connect the two villages, but the giants living on Ledo Island in the center keep wading out across the Silt Sea to destroy the bridge

Draj (based on Aztec culture)

    The Mighty and Omnipotent Tectuktitlay, Father of Life and Master of the Two Moons claims to be a living god
    Templars in Draj are known as Moon Priests
    The fertile soil surrounding Draj allows it to grow many crops, including grain for bread and hemp, which makes for good ropes
    Draj is almost constantly at war, raiding villages and even other city states for captives to be sacrificed on the steps of Tectuktitlay’s pyramid, overlooking the gladiatorial arena
    Knowledge of history is expressly forbidden by Tectuktitlay, nothing beyond mortal memory is really known about the past of this city
    Draji warriors decorate themselves with the skins of various beasts and animals, and carry obsidian-edged clubs called Macuahuitl as well as short harpoons
    Criminals in Draj receive only one sentence: death, either by execution or by caging (a very slow death by exposure).
    Crime, especially theft is so looked down upon by Draji culture that most citizens would rather sell themselves into slavery than steal.
    Instead of a wall, the entrance to the city state is surrounded by expansive mud flats, which provide plenty of protection from invaders.
    Rumor: Draj has vast storehouses of grains and hemp that it keeps hidden from everybody in order to drive up their prices when trading with other city states.

Gulg (based on various African savannah cultures)

    Lalali-Puy, the oba, or forest goddess is the only ruler of a city state who enjoys the popular support of her people
    Gulg lies at the southern end of the Crescent Forest
    Nearly everything in Gulg is made from Agafari wood, even the houses are carved out of the very trees
    Lalali-Puy controls all economic activity within Gulg directly, taking all the food produced and distributing it amongst her people. Merchants from outside the city can trade with the city state, but it is forbidden to trade with the citizens themselves.
    Citizens of Gulg also have the right to appeal directly to Lalai-Pui for an audience if they need a matter resolved.
    Gulg’s city wall is a magically infused hedge of thorny brambles that actively seek out the flesh of those who try to penetrate it.
    Despite what the title of city state invokes, Gulg is actually a collection of villages all crammed together within the shelter of the city wall
    When a new Nganga (templar) is chosen, the district they come from holds a funeral service to symbolize that the citizen they once were is no more.
    The templars of Gulg wear masks or face paint to hide their features and strike fear into those who would oppose the Oba
    Rumor: If not for the power of the Oba and her Judagas (warriors), Nibenay would likely have destroyed or taken Gulg over long ago.

Nibenay (based on Angkor culture)

    Nobody can remember the last time Nibenay, the Shadow King was seen outside the Naggaramakam
    The Naggaramakam is a walled central district in which only Nibenay’s Templars may enter and leave. Slaves who enter here are never permitted to leave again
    Nibenay lies at the northern end of the Crescent Forest
    Every surface of every building in Nibenay is covered with carvings of various figures
    Nibenay holds the only permanent Elven market, which is run by the Sky Singers tribe
    The Monastery of the Exalted Path is an all male psionics academy, the female counterpart is called The Monastery of Serene Bliss. Both are well respected
    A line of large statues of King Nibenay stand on each side of the main road to the city. The statues are called the Omnipotent Receivers as it is believed that the Shadow King can see through their eyes.
    Some people believe that the Shadow King hasn’t been seen because he actually died a long time ago.
    All Nibenese templars are female and are sometimes referred to as Nibenay’s Wives
    Rumor: the ruins of Giustenal are said to contain a powerful psionic entity

Raam (based on ancient Indian and Egyptian culture)

    The Great Vizier Abalach-Re claims to be the emissary of a higher power known as Badna
    Abalach-Re assures citizens that Badna watches her closely and will strike her down if she falters in her duties, but few believe her.
    Almost no citizens of Raam actually respect their Sorcerer Queen, and there is open talk of rebellion in the streets
    The nobles of Raam are little more than warlords constantly fighting against each other and jockeying for position in the inevitable revolution
    Templars of Raam almost never travel alone, lest they are murdered in the streets
    Raam culture consists of a rigid caste system
    While it was once an economic powerhouse, and still remains the largest city-state on the tablelands, Raam’s infrastructure has fallen almost completely apart due to the indifference of Abalach-Re who prefers to take pleasure in whatever strikes her fancy rather than rule her city.
    Crime runs rampant in the streets without the presence of templars to maintain order.
    Abalach-Re has born hundreds of illegitemate children over the 30 or so generations that she has ruled Raam. Known as the Offspring, many of her children have exhibited unusual psionic and arcane talents.
    Rumor: Stay away from the ruins of Yaramuke. Hamanu of Urik used such foul magics to destroy it that the entire area, including the fresh water springs that flow from within are all posionous

Tyr (based on the culture of Tyre)

    King Kalak, the Tyrant of Tyr has allocated an inordinate number of slaves towards working to build his ziggurat, including those owned by the nobility
    Even the iron mines, upon which Tyr’s economy is based have been shut down to allocate more resources to the ziggurat
    Nobody knows what the ziggurat is for
    Kalak’s Templars as well as his personal guard are all armed with iron swords
    As in most of the city states, while Tyr’s Elven Market is always in the same area, the vendors are always changing from one day to the next.
    Because most of the slave laborers have been working on the ziggurat, the remaining gladiatorial slaves have been putting on more and more impressive fights, rather than the barbarically uneven matches that were normally seen before. This in turn is increasing the draw that the games have to the point where seat prices have risen dramatically.
    People are starting to whisper that King Kalak has gone mad.
    Tyr is located in a valley along the edge of the Ringing Mountains
    Taxes have also risen dramatically since Kalak began the construction of his ziggurat.
    Rumor: Tyr was built atop the ruined foundations of an ancient city. Though many of the passages and byways are blocked off either by more recent construction, or shifting dunes, there are still many hidden access points to various locations under the city. This area is known as UnderTyr.

Urik (based on Babylonian culture)

    King Hamanu trains daily with his warriors, even the slaves
    The walls of Urik are famous for being nearly unbreachable
    You would do well to remember all of Hamanu’s many laws if you don’t want to find yourself being sold into slavery by a templar
    Urik lies near the Dragon’s Bowl - a massive crater with 1000 foot high cliffs leading down to a large lake in the bottom.
    The majority of the tools and weapons found in Urik are made from obsidian, which is mined from the nearby Smoking Crown mountains.
    Statues of lions top the massive walls, where guards patrol with their bows and obsidian-tipped arrows
    Urik’s gladiatorial arena, known as the Pit of Black Death, rests in an old abandoned obsidian mine, its walls lined with razor sharp obsidian.
    Children are tested by templars at an early age and are assigned a vocation based on their abilities. It is extremely rare for a change in career in Urik.
    Children who show talent in The Way are taken from their parents and sent to Hamanu’s school of the mind for training.
    Rumor: King Kalak of Tyr has stopped production of iron, Hamanu might send his army to get more iron!

