\input{specialisations/arcana}
\input{specialisations/archer}
\input{specialisations/assassin}
%\input{specialisations/beast_rider}
%\input{specialisations/bodyguard}
\input{specialisations/charmer}
%\input{specialisations/con_artist}
%\input{specialisations/diplomat}
%\input{specialisations/enforcer}
\input{specialisations/gladiator}
%\input{specialisations/hunter}
\input{specialisations/mercenary}
%\input{specialisations/nomad}
\input{specialisations/performer}
\input{specialisations/doctor}
\input{specialisations/primal}
\input{specialisations/psion}
%\input{specialisations/raider}
%\input{specialisations/scholar}
%\input{specialisations/scout}
%\input{specialisations/soul_blade}
\input{specialisations/thief}
%\input{specialisations/trader}

\chapter{Specialisations}\label{chap:specs}

\epigraph{\textit{
"There are many paths to power, but all power comes at a price. Fame or infamy follows those who make great sacrifices
and who reach grand achievements. Would you be called tyrant or savior, I wonder. Perhaps you would prefer to be
addressed as Mighty One, or plain and simply by your birthname? Will the bards speak of you as delusional or
omnipotent? It all depends on the eye that sees. The hero of one is villain to another. But all beings of power share one
trait -each has its own secrets. Remnants of the past, stories of the now, or visions of the future - secrets are the source of
power. And the keepers of the greatest secrets are the most dangerous of all beings, for they will use any means to prevent
others from unveiling them." } } { The Oracle, Blue Shrine Scrolls }

As stated in ~\cref{chap:creation} Each character combined two specialisations to form his or her career. In addition, it is
possible to buy new careers using experience points as mentioned in ~\tref{table:experience}.

\begin{multicols}{2}

\arcanaDescription
\archerDescription
\assassinDescription
%\beastRiderDescription
%\bodyguardDescription
\charmerDescription
%\con_artistDescription
%\diplomatDescription
%\enforcerDescription
\gladiatorDescription
%\hunterDescription
\mercenaryDescription
%\nomadDescription
\performerDescription
\doctorDescription
\primalDescription
\psionDescription
%\raiderDescription
%\scholarDescription
%\scoutDescription
%\soulBladeDescription
\thiefDescription
%\traderDescription

\end{multicols}

\section{Talent Trees}

\arcanaTree
\archerTree
\assassinTree
%\beastRiderTree
%\bodyguardTree
\charmerTree
%\con_artistTree
%\diplomatTree
%\enforcerTree
\gladiatorTree
%\hunterTree
\mercenaryTree
%\nomadTree
\performerTree
\doctorTree
\primalTree
\psionTree
%\raiderTree
%\scholarTree
%\scoutTree
%\soulBladeTree
\thiefTree
%\traderTree
