Psionic Mimic: At the GM's discresion, [CHARACTER] may make and opposed Charm or Deception versus Vigilance check as an action to pretend to be a friend, companion, loved one, or of the same species as its target.
Psionic Hunter: Roll [FORCE] on Initiative checks; [LIGHT]: gain [SUCCESS] per point on its initiative check
Psionic Stalker: Only works with Psionics rank 1+. Commit [FORCE]: gain [BOOST][BOOST] on Stealth checks
Telepathy: [CHARACTER] can communicate with other beings at Medium range using a simple form of telepathy.
Psionic Seer: [CHARACTER] occasionally sees glimpses of the future, letting them predict certain events even before they occur.
Psionic MindFog: Manouver to activate or sustain; while active, all enemies within short range add [THREAT] to all skill checks they make.
Psionic Shield: Maneuver to activate or deactivate; while active, gains defense 2, but [CHARACTER] cannot use the Move maneuver.
Psionic Leap: Once per encounter, a [CHARACTER] can use its free maneuver to move from medium range to engaged to attack a target. Along with allowing the [SPECIES] to close quickly with its prey, a charge also adds 2 damage to the attack.
Psionic Sensitivity: [CHARACTER] may make an Average Perception check to detect all Psionic-sensitive creatures or characters with a Psionics rating within medium range.
Psionic Illusion: Combat checks targeting [CHARACTER] always use Willpower in place of the characteristic normally associated with that skill.
Psionic Disguise: As an action, a [CHARACTER] may suffer 3 strain and make an [AVERAGE] Resilience check. If [CHARACTER] succeeds, she changes appearance to match that of a silhouette 1 character whom she has observed before. An observing character must make opposed Perception vs Deception check to detect that something is amiss with the impersonated character's likeness, mannerisms, or behavior. As always, the GM can add [BOOST] or [SETBACK] for situational effects that might affect the check.
Psionic Manipulation: [CHARACTER] can affect emotional states of other sentients. Once per check as an incidental, [CHARACTER] may suffer 2 strain to upgrade the ability of a Charm, Deception, or Negotiation check against a living sentient being within short range once.
Psionic Pounce: If the [CHARACTEr] uses the aim maneuver, it also gains Knockdown on its next attack.
