\newcommand\psionicFarsightTitle{ Farsight (Power)}
\newcommand\psionicFarsightDescription{
    The Force user expands normal visual sense through a connection to the Force.
    The Force user may spend \darklight to ignore the effects of darkness or blindness and see normally at up to medium range for the remainder
    of the round (or one minute). This allows the user to view everthing most sentients could normally be able to see on a well lit day.
}
\newcommand\psionicFarsightTalent{ \Talent[name=\psionicFarsightTitle, active=false, ranked=true]{\psionicFarsightDescription} }

\newcommand\farsightDurationTitle{ Farsight Duration}
\newcommand\farsightDurationDescription{ Spend \darklight to increase duration by number of rounds or minutes equal to Duration upgrades purchased. }
\newcommand\farsightDurationTalent{ \Talent[name=\farsightDurationTitle, active=false, ranked=true]{\farsightDurationDescription} }

\newcommand\farsightControlATitle{ Farsight Control 1}
\newcommand\farsightControlADescription{ Spend \darklight to see microscopic details of a single object within engaged range. }
\newcommand\farsightControlATalent{ \Talent[name=\farsightControlATitle, active=false, ranked=true]{\farsightControlADescription} }

\newcommand\farsightControlBTitle{ Farsight Control 2}
\newcommand\farsightControlBDescription{ Spend \darklight to see through a single object at medium range as through it were transparent. }
\newcommand\farsightControlBTalent{ \Talent[name=\farsightControlBTitle, active=false, ranked=true]{\farsightControlBDescription} }

\newcommand\farsightControlCTitle{ Farsight Control 3}
\newcommand\farsightControlCDescription{ Spend \darklight to make out fine details on a single object within medium range. }
\newcommand\farsightControlCTalent{ \Talent[name=\farsightControlCTitle, active=false, ranked=true]{\farsightControlCDescription} }

\newcommand\farsightControlDTitle{ Farsight Control 4}
\newcommand\farsightControlDDescription{ When making a Vigilance or Perception check, make a Farsight power check as part of the pool and spend \darklight to gain \success or \advantage on the check. }
\newcommand\farsightControlDTalent{ \Talent[name=\farsightControlDTitle, active=false, ranked=true]{\farsightControlDDescription} }

\newcommand\farsightControlETitle{ Farsight Control 5}
\newcommand\farsightControlEDescription{ This power gains the ongoing effect: Commit \force after sucessfully activating the Farsight power to increase ranks in Perception by 1. }
\newcommand\farsightControlETalent{ \Talent[name=\farsightControlETitle, active=false, ranked=true]{\farsightControlEDescription} }

\newcommand\farsightControlFTitle{ Farsight Control 6}
\newcommand\farsightControlFDescription{ Spend \darklight\darklight to see in every direction simultaneously, noticing and observings things in a full 360 arc.  }
\newcommand\farsightControlFTalent{ \Talent[name=\farsightControlFTitle, active=false, ranked=true]{\farsightControlFDescription} }

\newcommand\farsightRangeTitle{ Farsight Range}
\newcommand\farsightRangeDescription{ Spend \darklight to increase the power's range by a number of range bands equal to Range upgrades purchased. }
\newcommand\farsightRangeTalent{ \Talent[name=\farsightRangeTitle, active=false, ranked=true]{\farsightRangeDescription} }

\newcommand\farsightMasteryTitle{ Farsight Mastery}
\newcommand\farsightMasteryDescription{ 
    Spend \darklight\darklight. The user can now see as thought from a spot
    within close range of the user's body.
}
\newcommand\farsightMasteryTalent{ \Talent[name=\farsightMasteryTitle, active=false, ranked=true]{\farsightMasteryDescription} }

