\newcommand\psionicImbueTitle{ Imbue (Power)}
\newcommand\psionicImbueDescription{
    The Force user lends strength to allies, making them more potent, resourceful, or resilient for a time.
    The user may spend FF to increase one of another engaged character’s characteristics by 1 (to a max of 6) until the end of the Force
    user’s next turn. This can only be used once per character per encounter. If the user uses z to generate F, the tagret increases a
    second characteristic by 1 (to a max of 6) until the end of the user’s next turn, but both the Force user and target suffer 3 strain.
}
\newcommand\psionicImbueTalent{ \Talent[name=\psionicImbueTitle, active=false, ranked=true]{\psionicImbueDescription} }

\newcommand\imbueDurationATitle{ Imbue Duration 1}
\newcommand\imbueDurationADescription{ Commit \force\force to sustain the effects of this power as long as the target remains in range.  }
\newcommand\imbueDurationATalent{ \Talent[name=\imbueDurationATitle, active=false, ranked=true]{\imbueDurationADescription} }

\newcommand\imbueDurationBTitle{ Imbue Duration 2}
\newcommand\imbueDurationBDescription{ Commit \force to sustain the effects of this power as long as the target remains in range. }
\newcommand\imbueDurationBTalent{ \Talent[name=\imbueDurationBTitle, active=false, ranked=true]{\imbueDurationBDescription} }

\newcommand\imbueControlTitle{ Imbue Control}
\newcommand\imbueControlDescription{ Spend F to allow the target to count as having ranks in a skill equal to users ranks in the skill. }
\newcommand\imbueControlTalent{ \Talent[name=\imbueControlTitle, active=false, ranked=true]{\imbueControlDescription} }

\newcommand\imbueRangeTitle{ Imbue Range}
\newcommand\imbueRangeDescription{ Spend FF to increase the power’s range by a number of range bands equal to Range upgrades purchased. }
\newcommand\imbueRangeTalent{ \Talent[name=\imbueRangeTitle, active=false, ranked=true]{\imbueRangeDescription} }

\newcommand\imbueStrengthTitle{ Imbue Strength}
\newcommand\imbueStrengthDescription{
    In no z were used to generate F, decrease all Critical Inuries
    suffered and inflicted by 10 per Strength upgrade purchases. If
    no Z were used to generate F, increase all Critical Injuries
    suffered and inflicted by 10 per Strength upgrade purchased.
}
\newcommand\imbueStrengthTalent{ \Talent[name=\imbueStrengthTitle, active=false, ranked=true]{\imbueStrengthDescription} }

\newcommand\imbueMasteryTitle{ Imbue Mastery}
\newcommand\imbueMasteryDescription{ 
    Spend F to allow the target
    to count as having ranks in a
    skill equal to users ranks in
    the skill.
}
\newcommand\imbueMasteryTalent{ \Talent[name=\imbueMasteryTitle, active=false, ranked=true]{\imbueMasteryDescription} }

