\newcommand\psionicMoveTitle{ Move (Power)}
\newcommand\psionicMoveDescription{
    The Psionic can restrain one target, preventing it from acting.\\
    The character may spend \darklight to immobilize a target within short range until the end of the character's next turn.
    If the character used any \dark to generate \darklight, the target also suffers 1 wound per \darklight spent on the
    check (ignoring soak).
}
\newcommand\psionicMoveTalent{ \Talent[name=\psionicMoveTitle, active=false, ranked=true]{\psionicMoveDescription} }

\newcommand\moveDurationTitle{ Move Duration}
\newcommand\moveDurationDescription{ Commit \force\force\force to sustain the ongoing effects of the power on each affected target. }
\newcommand\moveDurationTalent{ \Talent[name=\moveDurationTitle, active=false, ranked=true]{\moveDurationDescription} }

\newcommand\moveControlTitle{ Move Control}
\newcommand\moveControlDescription{ Spend \darklight. While affected by Move, a target suffers strain equal to the user's Willpower whenever the target takes an action.  }
\newcommand\moveControlTalent{ \Talent[name=\moveControlTitle, active=false, ranked=true]{\moveControlDescription} }

\newcommand\moveMagnitudeTitle{ Move Magnitude}
\newcommand\moveMagnitudeDescription{ Spend \darklight\darklight to affect 1 additional target within range per rank of Magnitude purchased.  }
\newcommand\moveMagnitudeTalent{ \Talent[name=\moveMagnitudeTitle, active=false, ranked=true]{\moveMagnitudeDescription} }

\newcommand\moveRangeTitle{ Move Range}
\newcommand\moveRangeDescription{ Spend \darklight to increase power’s range by a number of range bands equal to Range upgrades purchased.  }
\newcommand\moveRangeTalent{ \Talent[name=\moveRangeTitle, active=false, ranked=true]{\moveRangeDescription} }

\newcommand\moveStrengthTitle{ Move Strength}
\newcommand\moveStrengthDescription{ Spend \darklight to disorient the target for a number of rounds equal to Strength upgrades purchased.  }
\newcommand\moveStrengthTalent{ \Talent[name=\moveStrengthTitle, active=false, ranked=true]{\moveStrengthDescription} }

\newcommand\moveMasteryTitle{ Move Mastery}
\newcommand\moveMasteryDescription{ 
    When the Psionic is making a Move power check, if the check was not already opposed, the character may
    roll an opposed Discipline vs. Discipline check against one target of the power. If no \dark were used
    to generate \darklight and the user succeeds on the check, he may immediately stagger the target until
    the end of his next turn. If any \dark were used to generate \darklight and the check succeeds, the target
    suffers a Critical Injury, adding +10 to the roll per \darklight spent on the check.
}
\newcommand\moveMasteryTalent{ \Talent[name=\moveMasteryTitle, active=false, ranked=true]{\moveMasteryDescription} }

